---
title: "Disease_models"
output: html_notebook
---

# Statistics for Acropora diseases at NFI 

# Statistics 

Transect-level statistical analysis on disease dynamics. 

2) Disease prevalence (DP) (% of surveyed community showing active disease signs)
    a) Build glm (use weights function to specify number of colonies per transect), family = binomial
3) Disease severity (DS) (the best variable for this response needs to be assessed)
    b) Step two: Build model (lm, average is normally distributed)
Predictor variables for models in 2) and 3):
+ TP (Dec,April)
+ Site (EB,SB)
+ Total Acropora cover (%)
+ TP*Site interaction (for Syndrome type diseases only)

Load libraries
```{r}
# Libraries 
library(ggplot2)
library(dplyr)
library(tidyr)
library(multcomp)
library(lme4)
library(effects)
library(lmerTest)
library(afex)
library(car)
library(magrittr)
library(ggeffects)
library(sjmisc)
library(splines)
library(glmmTMB)
library(DHARMa)
library(devtools)
library(pbkrtest)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(MASS)
library(lsmeans)
library(MuMIn)

```


# DP (Disease prevalence)
Files contain prevalence, colony abundance and cover for lagoonal transects (EB, SB) over time.

```{r}

# Subacute-acute WS
acute_prev_modelling <- read.csv("Acute_prev_modelling.csv")

# Paling WS with tissue loss 
chronic_prev_modelling <- read.csv("Chronic_prev_modelling.csv")

# Paling Syndrome
paling_prev_modelling <- read.csv("Paling_prev_modelling.csv")

# GA_prev_modelling 
GA_prev_modelling <- read.csv("GA_prev_modelling.csv")

```


Health state: Paling syndrome prevalence 

```{r}

# Calculate mean prevalence across the whole lagoon at each time point 

paling_prev_modelling$abundance <- as.numeric(paling_prev_modelling$abundance)

# Remove 0 weights from datasets 

paling_prev_nozero <- paling_prev_modelling[paling_prev_modelling$abundance != 0, ]    

paling_prev_nozero$Month <- as.factor(paling_prev_nozero$Month)
paling_prev_nozero$Site <- as.factor(paling_prev_nozero$Site)

str(paling_prev_nozero)
moda <- glm(Paling_prev_prop ~ Site * Month + Acropora_cover, weights = abundance, family = binomial(), data=paling_prev_nozero)

simulationOutput <- simulateResiduals(fittedModel = moda, plot = F)
residuals(simulationOutput)

testZeroInflation(simulationOutput)

plot(simulationOutput)

summary(moda)
Anova(moda)

# Site x Month interaction 
# Site x Acro cover 
# Month x Acro cover 

library(MuMIn)
r.squaredGLMM(moda)

library(lsmeans)
lsmeans(moda, pairwise ~  Month, adjust = "Tukey")

```

Plotting 

```{r}

# Errors dot plot 

acro_all_paling <- paling_prev_nozero %>% group_by(Month) %>%
  summarise(mean = mean(Paling_prev_prop, na.rm = TRUE),
            sd = sd(Paling_prev_prop, na.rm = TRUE),
            n = sum(!is.na(Paling_prev_prop)),
            se = sd/sqrt(n))

acro_all_paling$Month <- factor(acro_all_paling$Month, levels = c("April_2021","April_2022","Sept_2022","Dec_2022","April_2023"))

ggplot(acro_all_paling, aes(x=Month, y=mean)) + 
    geom_point(position = position_dodge(0.8), colour = "#960019") +
  geom_line() +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8), colour = "#960019") +
    scale_y_continuous(limits = c(0,0.4)) +
  theme_bw() 

```


Paling WS with Tissue Loss
```{r}
# Test for how many 0's are present 

# Calculate mean prevalence across the whole lagoon at each time point 

# Remove 0 weights from datasets 

chronic_prev_nozero <- chronic_prev_modelling[chronic_prev_modelling$abundance != 0, ]    

chronic_prev_nozero %>% ungroup() %>% summarise(mean_lagoon = mean(Chronic_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Chronic_prev_prop)),
          sd = sd(Chronic_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

# Across all lagoon with time
chronic_prev_nozero%>% ungroup() %>% group_by(Month) %>% summarise(mean_lagoon = mean(Chronic_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Chronic_prev_prop)),
          sd = sd(Chronic_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

# Across all lagoon with time
chronic_prev_nozero%>% ungroup() %>% group_by(Month,Site) %>% summarise(mean_lagoon = mean(Chronic_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Chronic_prev_prop)),
          sd = sd(Chronic_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

100*sum(chronic_prev_modelling$Chronic_prev_prop == 0)/nrow(chronic_prev_modelling)

str(chronic_prev_modelling)

chronic_prev_modelling$abundance <- as.numeric(chronic_prev_modelling$abundance)



chronic_prev_nozero$Month <- as.factor(chronic_prev_nozero$Month)
chronic_prev_nozero$Site <- as.factor(chronic_prev_nozero$Site)


mod1 <- glm(Chronic_prev_prop ~ Site * Month + Acropora_cover, weights = abundance, family = binomial(), data=chronic_prev_nozero)

simulationOutput <- simulateResiduals(fittedModel = mod1, plot = F)
residuals(simulationOutput)

testZeroInflation(simulationOutput)

plot(simulationOutput)

summary(mod1)
Anova(mod1)


r.squaredGLMM(mod1)


lsmeans(mod1, pairwise ~ Site | Month, adjust = "Tukey")
lsmeans(mod1, pairwise ~ Month | Site, adjust = "Tukey")

Anova(mod1)%>% as.data.frame() %>% write.csv(file = "Chronic_prev_anova.csv")
anova(mod1, test = "Chisq") %>% as.data.frame() %>% write.csv(file = "Chronic_prev_anova.csv")


```
Plotting

```{r}
# Across all lagoon with time
acro_chronic_lagoon_filtered_plot <- chronic_prev_nozero%>% group_by(Month,Site) %>% summarise(mean = mean(Chronic_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Chronic_prev_prop)),
          sd = sd(Chronic_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

acro_chronic_lagoon_filtered_plot$Month <- factor(acro_chronic_lagoon_filtered_plot$Month, levels = c("April_2021","April_2022","Sept_2022","Dec_2022","April_2023"))
acro_chronic_lagoon_filtered_plot$Site <- factor(acro_chronic_lagoon_filtered_plot$Site, levels = c("SB","EB"))

ggplot(acro_chronic_lagoon_filtered_plot, aes(x=Month, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
  geom_line() +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.4)) +
  theme_bw() +
  facet_wrap(~Site) +
  scale_color_manual(values =  c("#f5c578", "#e05f15"))
```

Acute-subacute WS

```{r}
# Remove 0 weights from datasets 

acute_prev_nozero <- acute_prev_modelling[acute_prev_modelling$abundance != 0, ]    
str(acute_prev_nozero)

# Calculate mean prevalence across the whole lagoon at each time point 
str(acute_prev_nozero)

acute_prev_nozero %>% ungroup() %>% summarise(mean_lagoon = mean(Acute_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Acute_prev_prop)),
          sd = sd(Acute_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

# Across all lagoon with time
acute_prev_nozero %>% ungroup() %>% group_by(Month) %>% summarise(mean_lagoon = mean(Acute_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Acute_prev_prop)),
          sd = sd(Acute_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

acute_prev_nozero %>% ungroup() %>% group_by(Month,Site) %>% summarise(mean_lagoon = mean(Acute_prev_prop, na.rm = TRUE),
          n = sum(!is.na(Acute_prev_prop)),
          sd = sd(Acute_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

mod3 <- glm(Acute_prev_prop ~ Site * Month + Acropora_cover, weights = abundance, family = binomial(), data=acute_prev_nozero)

simulationOutput <- simulateResiduals(fittedModel = mod3, plot = F)
residuals(simulationOutput)

plot(simulationOutput)
# No problems detected 

summary(mod3)
anova(mod3, test = "Chisq") %>% as.data.frame() %>% write.csv(file = "Acute_prev_anova.csv")
Anova(mod3)%>% as.data.frame() %>% write.csv(file = "Acute_prev_anova.csv")
# Site x Month interaction 
# Site x Acro cover 
# Month x Acro cover 

r.squaredGLMM(mod3)

lsmeans(mod3, pairwise ~ Site | Month, adjust = "Tukey")
lsmeans(mod3, pairwise ~ Month | Site, adjust = "Tukey")

```

```{r}

str(acute_prev_nozero)

# Errors dot plot 
acro_acute_lagoon_filtered_plot <- acute_prev_nozero %>% group_by(Month,Site) %>%
  summarise(mean = mean(Acute_prev_prop, na.rm = TRUE),
            sd = sd(Acute_prev_prop, na.rm = TRUE),
            n = sum(!is.na(Acute_prev_prop)),
            se = sd/sqrt(n))

acro_acute_lagoon_filtered_plot$Month <- factor(acro_acute_lagoon_filtered_plot$Month, levels = c("April_2021","April_2022","Sept_2022","Dec_2022","April_2023"))

acro_acute_lagoon_filtered_plot$Site <- factor(acro_acute_lagoon_filtered_plot$Site, levels = c("SB","EB"))

ggplot(acro_acute_lagoon_filtered_plot, aes(x=Month, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.6)) +
  theme_bw() +
  scale_color_manual(values =  c("#b2dbed", "#42b0cc"))

ggplot(acro_acute_lagoon_filtered_plot, aes(x=Month, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.8)) +
  theme_bw() +
  facet_wrap(~Site) +
  scale_color_manual(values =  c("#b2dbed", "#42b0cc"))
```


GA

```{r}

# Remove 0 weights from datasets 

GA_prev_nozero <- GA_prev_modelling[GA_prev_modelling$abundance != 0, ]    
str(GA_prev_nozero)

GA_prev_nozero %>% ungroup() %>% summarise(mean_lagoon = mean(GA_prev_prop, na.rm = TRUE),
          n = sum(!is.na(GA_prev_prop)),
          sd = sd(GA_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

# Across all lagoon with time
GA_prev_nozero %>% ungroup() %>% group_by(Site) %>% summarise(mean_lagoon = mean(GA_prev_prop, na.rm = TRUE),
          n = sum(!is.na(GA_prev_prop)),
          sd = sd(GA_prev_prop, na.rm = TRUE),
          se = sd/sqrt(n))

mod5 <- glm(GA_prev_prop ~ Site + Month + Acropora_cover, weights = abundance, family = binomial(), data=GA_prev_nozero)

simulationOutput <- simulateResiduals(fittedModel = mod5, plot = F)
residuals(simulationOutput)

plot(simulationOutput)

testDispersion(simulationOutput)
testZeroInflation(simulationOutput)
testResiduals(simulationOutput)
anova(mod5, test = "Chisq")

plot_model(mod5, type = "pred", terms = "Acropora_cover",show.values = TRUE, show.data = TRUE,show.intercept = TRUE) +
  theme_bw()

r.squaredGLMM(mod5)

# Try transforming the cover variable (logit )
library(car)

logit(GA_prev_nozero$Acropora_cover, percents = TRUE)

# Try a negative binomial model

negative_binomial_GA <- GA_prev_nozero %>% mutate(diseased = abundance*GA_prev_prop)

mode6 <- glmmTMB(diseased ~ Site + Month + Acropora_cover, offset = log(abundance) , data = negative_binomial_GA, family = nbinom2())

simulationOutput <- simulateResiduals(fittedModel = mode6, plot = F)
residuals(simulationOutput)

plot(simulationOutput)

Anova(mode6) %>% as.data.frame() %>% write.csv(file = "GA_prev_anova.csv")

r.squaredLR(mode6)
r.squaredGLMM(mode6)

library(jtools)
effect_plot(mode6, pred = Acropora_cover, interval = TRUE, plot.points = F, rug = TRUE,
            jitter = 0.05)

plot(allEffects(mode6))

plot_model(mode6, type = "pred", terms = "Acropora_cover",show.values = TRUE, show.data = TRUE) +
  theme_bw()
plot_model(mode6, type = "pred", terms = "Site",show.values = TRUE, show.data = TRUE) +
  theme_bw()

emm <- emmeans(mode6, specs="Acropora_cover")
emm
summary(mode6)

mode6$coefficients

# Site x Month interaction 
# Site x Acro cover 
# Month x Acro cover 

r.squaredGLMM(mod3)

lsmeans(mode6, pairwise ~ Site, adjust = "Tukey")

```

```{r}

View(GA_prev_nozero)

GA_prev_nozero$Month <- factor(GA_prev_nozero$Month, levels = c("April_2021","April_2022","Sept_2022","Dec_2022","April_2023"))

GA_prev_nozero$Site <- factor(GA_prev_nozero$Site, levels = c("SB","EB"))

# Errors dot plot 
acro_GA_lagoon_filtered_plot <- GA_prev_nozero %>% group_by(Month,Site) %>%
  summarise(mean = mean(GA_prev_prop, na.rm = TRUE),
            sd = sd(GA_prev_prop, na.rm = TRUE),
            n = sum(!is.na(GA_prev_prop)),
            se = sd/sqrt(n))

ggplot(acro_GA_lagoon_filtered_plot, aes(x=Month, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.4)) +
  facet_wrap(~Site) +
  theme_bw() +
  scale_color_manual(values =  c("#9DC183","#0A6522"))

ggplot(acro_GA_lagoon_filtered_plot, aes(x=Site, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
  geom_line() +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.4)) +
  theme_bw() +
  scale_color_manual(values =  c("#9DC183","#0A6522"))

```

# DS (Disease severity)

```{r}

chronic_sev_modelling <- read.csv("acro_chron_sev.csv") 
acute_sev_modelling <- read.csv("Acute_severity_modelling.csv")
GA_sev_modelling <- read.csv("GA_severity_modelling.csv")

```

Paling WS with Tissue Loss 

```{r}

str(chronic_sev_modelling)

# Make a half violin plot of disease severity 

chronic_sev_modelling$Month <- as.factor(chronic_sev_modelling$Month)
chronic_sev_modelling$Site <- as.factor(chronic_sev_modelling$Site)
chronic_sev_modelling$Survey <- as.factor(chronic_sev_modelling$Survey)

chronic_sev_modelling %>% summarise(min_sev = min(Severity),
                                    max_sev = max(Severity))

chronic_sev_modelling %>% ungroup() %>% summarise(mean_sev_lagoon = mean(Severity),
     n = sum(!is.na(Severity)),
          sd = sd(Severity, na.rm = TRUE),
          se = sd/sqrt(n))

chronic_sev_modelling %>% group_by(Month) %>% summarise(mean_sev_lagoon = mean(Severity),
     n = sum(!is.na(Severity)),
          sd = sd(Severity, na.rm = TRUE),
          se = sd/sqrt(n))


# Try and model it as a count variable using poison

model_2<- lmer(log(Severity) ~  Site * Month + (1|Survey), data=chronic_sev_modelling)

simulationOutput <- simulateResiduals(fittedModel = model_2, plot = F)
residuals(simulationOutput)

plot(simulationOutput)

summary(model_2)

Anova(model_2) %>% as.data.frame() %>% write.csv(file = "Chronic_sev_anova.csv")
r.squaredGLMM(model_2)

lsmeans(model_2, pairwise ~ Site | Month, adjust = "Tukey")
lsmeans(model_2, pairwise ~ Month | Site, adjust = "Tukey")



```
Plotting
```{r}

chronic_sev_modelling$Month <- factor(chronic_sev_modelling$Month, levels = c("2021_April","2022_April","2022_September","2022_December","2023_April"))

chronic_sev_modelling$Site <- factor(chronic_sev_modelling$Site, levels = c("SB","EB"))


ggplot(acro_acute_lagoon_filtered_plot, aes(x=Month, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.6)) +
  theme_bw() +
  scale_color_manual(values =  c("#b2dbed", "#42b0cc"))

ggplot(chronic_sev_modelling, aes(x=Month, y=Severity, color = Site)) + 
    geom_boxplot(position = position_dodge(0.8)) +
    #geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    #scale_y_continuous(limits = c(0,0.8)) +
  theme_bw() +
  facet_wrap(~Site) +
  scale_color_manual(values =  c("#f5c578", "#e05f15"))

ggplot(chronic_sev_modelling, aes(x=Month, y=Severity, color = Site)) + 
    geom_boxplot(position = position_dodge(0.8)) +
    #geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    #scale_y_continuous(limits = c(0,0.8)) +
  theme_bw() +
  facet_wrap(~Site) +
  scale_color_manual(values =  c("#f5c578", "#e05f15"))


  

```

```{r}
str(acute_sev_modelling)

hist(acute_sev_modelling$Severity)

acute_sev_modelling$Month <- as.factor(acute_sev_modelling$Month)
acute_sev_modelling$Site <- as.factor(acute_sev_modelling$Site)
acute_sev_modelling$Survey <- as.factor(acute_sev_modelling$Survey)

acute_sev <- as.data.frame(acute_sev_modelling) %>%
 group_by(Month,Site,Survey) %>% summarise(mean_sev = mean(Severity))

acute_sev_modelling %>% summarise(min_sev = min(Severity),
                                    max_sev = max(Severity))

acute_sev %>% ungroup() %>% summarise(mean_sev_lagoon = mean(mean_sev),
     n = sum(!is.na(mean_sev)),
          sd = sd(mean_sev, na.rm = TRUE),
          se = sd/sqrt(n))

acute_sev %>% group_by(Month) %>% summarise(mean_sev_lagoon = mean(mean_sev),
     n = sum(!is.na(mean_sev)),
          sd = sd(mean_sev, na.rm = TRUE),
          se = sd/sqrt(n))

acute_sev %>% group_by(Month,Site) %>% summarise(mean_sev_lagoon = mean(mean_sev),
     n = sum(!is.na(mean_sev)),
          sd = sd(mean_sev, na.rm = TRUE),
          se = sd/sqrt(n))

hist(acute_sev$mean_sev)

model_3 <- lm(mean_sev ~  Site * Month, data=acute_sev)

plot(model_2)
summary(model_2)

Anova(model_2, test = "Chisq")

lsmeans(model_2, pairwise ~ Site | Month, adjust = "Tukey")
lsmeans(model_2, pairwise ~ Month | Site, adjust = "Tukey")

model_4<- lmer(log(Severity) ~  Site * Month + (1|Survey), data=acute_sev_modelling)

simulationOutput <- simulateResiduals(fittedModel = model_4, plot = F)
residuals(simulationOutput)

plot(simulationOutput)

Anova(model_4, test = "Chisq") %>% as.data.frame() %>% write.csv(file = "Acute_sev_anova.csv")

lsmeans(model_4, pairwise ~ Site | Month, adjust = "Tukey")
lsmeans(model_4, pairwise ~ Month | Site, adjust = "Tukey")

r.squaredGLMM(model_4)
```

```{r}

acute_sev_modelling$Month <- factor(acute_sev_modelling$Month, levels = c("April_2021","April_2022","Sept_2022","Dec_2022","April_2023"))

acute_sev_modelling$Site <- factor(acute_sev_modelling$Site, levels = c("SB","EB"))

ggplot(acro_acute_lagoon_filtered_plot, aes(x=Month, y=mean, color = Site)) + 
    geom_point(position = position_dodge(0.8)) +
    geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    scale_y_continuous(limits = c(0,0.6)) +
  theme_bw() +
  scale_color_manual(values =  c("#b2dbed", "#42b0cc"))

ggplot(acute_sev_modelling, aes(x=Month, y=Severity, color = Site)) + 
    geom_boxplot(position = position_dodge(0.8)) +
    #geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    #scale_y_continuous(limits = c(0,0.8)) +
  theme_bw() +
  facet_wrap(~Site) +
  scale_color_manual(values =  c("#b2dbed", "#42b0cc"))
```

# GA sev modelling 

```{r}

GA_sev_modelling %>% ungroup() %>% summarise(mean_sev_lagoon = mean(GA_area),
     n = sum(!is.na(GA_area)),
          sd = sd(GA_area, na.rm = TRUE),
          se = sd/sqrt(n))

GA_sev_modelling %>% group_by(Month) %>% summarise(mean_sev_lagoon = mean(GA_area),
     n = sum(!is.na(GA_area)),
          sd = sd(GA_area, na.rm = TRUE),
          se = sd/sqrt(n))

GA_sev_modelling %>% group_by(Month,Site) %>% summarise(mean_sev_lagoon = mean(GA_area),
     n = sum(!is.na(GA_area)),
          sd = sd(GA_area, na.rm = TRUE),
          se = sd/sqrt(n))


str(GA_sev_modelling)

GA_sev_modelling$Month <- as.factor(GA_sev_modelling$Month)
GA_sev_modelling$Site <- as.factor(GA_sev_modelling$Site)
GA_sev_modelling$Survey <- as.factor(GA_sev_modelling$Survey)

GA_sev <- as.data.frame(GA_sev_modelling) %>%
 group_by(Month,Site,Survey) %>% summarise(kax_sev = mean(GA_area))

GA_sev_modelling %>% ungroup() %>% summarise(max_sev = max(GA_area),
                                   min_sev = min(GA_area))


hist(GA_sev_modelling$GA_area)

model_2 <- lm(GA_area ~  Site * Month + mean_cover, data=GA_sev_modelling)
plot(model_2)
summary(model_2)

anova(model_2, test = "Chisq")

lsmeans(model_2, pairwise ~ Site | Month, adjust = "Tukey")
lsmeans(model_2, pairwise ~ Month | Site, adjust = "Tukey")

model_6<- lmer(log(GA_area) ~  Site * Month + (1|Survey), data=GA_sev_modelling)

simulationOutput <- simulateResiduals(fittedModel = model_6, plot = F)
residuals(simulationOutput)

plot(simulationOutput)
 
Anova(model_6, test = "Chisq") %>% as.data.frame() %>% write.csv(file = "GA_sev_anova.csv")

lsmeans(model_6, pairwise ~ Month, adjust = "Tukey")

r.squaredGLMM(model_6)


```


# Plot 

```{r}

GA_sev_modelling %>% group_by(Month) %>% summarise(mean_lagoon = mean(GA_area, na.rm = TRUE),
          n = sum(!is.na(GA_area)),
          sd = sd(GA_area, na.rm = TRUE),
          se = sd/sqrt(n))

GA_sev_modelling$Month <- factor(GA_sev_modelling$Month, levels = c("April_2021","April_2022","Sept_2022","Dec_2022","April_2023"))

ggplot(GA_sev_modelling, aes(x=Month, y=GA_area)) + 
    geom_boxplot(position = position_dodge(0.8), colour = "#0A6522") +
    #geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1,position = position_dodge(0.8)) +
    #scale_y_continuous(limits = c(0,0.8)) +
  theme_bw() #+
  scale_color_manual(values =  c("#b2dbed", "#42b0cc"))

```


